Analysis of cloud enhancement events in a 30-year record of global solar irradiance at Thessaloniki, Greece

### 2024-09-08 article/article.Rmd
Commit 2024-09-08 10:14

```{r example-day, echo=FALSE, fig.cap="Example of CE identification in Thessaloniki for 2019-07-11. The green line with blue symbols depicts the measured GHI in one minute steps. Red line shows the modelled threshold $E$ for the detection of CE events, which are denoted with red circles.Black curve represents the TOA TSI on horizontal plane.", fig.pos='H'}
knitr::include_graphics("../images/P-example-day-2.png")
```

>>>>

```{r example-day, echo=FALSE, fig.cap="Example of CE identification in Thessaloniki for 2019-07-11. The green line with blue symbols depicts the measured GHI in one minute steps. Red line shows the modelled threshold $E$ for the detection of CE events, which are denoted with red circles.Black curve represents the TOA TSI on horizontal plane.", fig.pos='H'}
knitr::include_graphics("../images/P-example-day-5.png")
```
